Karpov, Kasprov, Anand

### 2022-05-30 inst/kka.Rmd
bugfix

```{r,createchess3}
(chess3 <- f(o$par))
```

@@

```{r,label=savecurlingdataset,cache=TRUE}
save(kka,karpov_kasparov_anand,kka_3draws,kka_3whites,kka_array,chess3,file="kka.rda")
```

>>>>

```{r,createchess3}
jj <- round(o$par,2)
(chess3 <-  white_draw3(kka_array, lambda=jj[1],D=jj[2]))
```

@@

```{r,label=savecurlingdataset,cache=FALSE}
save(kka,karpov_kasparov_anand,kka_3draws,kka_3whites,kka_array,chess3,file="kka.rda")
```
